All Your Graphs Belong to Us

### 2012-07-17 doc/asplos13/method.tex
comment out UTS code snippet in eval

The metric we use is algorithmic time, which means startup and loading of the graph (from disk) is not included in the measurement.  Data is collected on real systems, which means minor variations in runtime exist from run to run.  The average of multiple runs are used, and where appropriate, confidence in the result is reported (error bars, standard deviation, etc).

@@

@@

>>>>

The metric we use is algorithmic time, which means startup and loading of the data structure (from disk) is not included in the measurement.  Data is collected on real systems, which means minor variations in runtime exist from run to run.  The average of multiple runs are used, and where appropriate, confidence in the result is reported (error bars, standard deviation, etc).

@@

The Grappa version of the in-memory tree search uses the asynchronous parallel for loop over a visited vertex's children list. A larger threshold can be set to take advantage of this locality by processing more child pointers sequentially in a single task.

@@

\paragraph{Breadth-first-search (BFS)} This is the primary kernel for the Graph500 benchmark and is what currently determines the ranking of machines on the Graph500 list~\cite{graph500list}. As a whole, the Graph500 benchmark suite is designed to bring the focus of system design on data-intensive workloads, particularly large-scale graph analysis problems, that are important among cybersecurity, informatics, and network understanding workloads. Graph500's definition of BFS of a graph consists of computing a search tree containing parent nodes for each traversed vertex during the search. While this is a relatively simple problem to solve, it exercises the random-access and fine-grained synchronization capabilities of a system as well as being a primitive in many other graph algorithms. Performance is measured in \emph{traversed edges per second} (TEPS), where the number of edges is the edges making up the generated BFS tree. One of the reference implementations of Graph500 BFS is for the XMT. We compare this against a straightforward Grappa implementation that algorithmically matches the XMT reference code to allow us to fairly compare the execution systems. We do not employ algorithmic improvements beyond the reference code, though there are many \cite{Beamer:Graph500,Yoo:FixedPointGraph500}.
